---
title: "PhenoCam Image Notebook"
author: "K Duffy"
date: "10/16/2019"
output: html_document
---
```{r}
library(data.table)
library(phenocamapi)
library(lubridate)
library(jpeg)
```
## Download midday images
While PhenoCam sites may have many images in a given day, many simple analyses
can use just the midday image when the sun is most directly overhead the canopy. 
Therefore, extracting a list of midday images (only one image a day) can be useful. 
```{r midday-list, fig.height=5, fig.width=8, message=FALSE}
# obtaining midday_images for HARV
HARV_middays <- get_midday_list('NEON.D01.HARV.DP1.00033')
# see the first few rows
head(HARV_middays)
```
Now we have a list of all the midday images from this Phenocam. Let's download
them and plot 
```{r midday-download, fig.height=5, fig.width=8}
# download a file
destfile <- tempfile(fileext = '.jpg')
# download only the first available file
# modify the `[1]` to download other images
download.file(HARV_middays[1], destfile = destfile, mode = 'wb')
# plot the image
img <- try(readJPEG(destfile))
if(class(img)!='try-error'){
  par(mar= c(0,0,0,0))
  plot(0:1,0:1, type='n', axes= FALSE, xlab= '', ylab = '')
  rasterImage(img, 0, 0, 1, 1)
}
```
### Download midday images for a given time range
Now we can access all the midday images and download them one at a time. However,
we frequently want all the images within a specific time range of interest. We'll
learn how to do that next. 
```{r midday-time-range, fig.height=6, fig.width=8, message=FALSE, eval=TRUE}
# open a temporary directory
tmp_dir <- tempdir()
# download a subset. Example NEON.D01.HARV.DP1.00033 2017
download_midday_images(site = 'NEON.D01.HARV.DP1.00033', # which site
                       y = 2017, # which year(s)
                       months = 1:12, # which month(s)
                       days = 15, # which days on month(s)
                       download_dir = tmp_dir) # where on your computer
# list of downloaded files
HARV_middays_path <- dir(tmp_dir, pattern = 'NEON.D01.HARV.DP1.00033*', full.names = TRUE)
head(HARV_middays_path)
```
We can demonstrate the seasonality of HARV forest observed from the camera. (Note
this code may take a while to run through the loop).
```{r plot-monthly-forest, fig.height=6, fig.width=8, message=FALSE, eval=TRUE}
n <- length(HARV_middays_path)
par(mar= c(0,0,0,0), mfrow=c(4,3), oma=c(0,0,3,0))
for(i in 1:n){
  img <- readJPEG(HARV_middays_path[i])
  plot(0:1,0:1, type='n', axes= FALSE, xlab= '', ylab = '')
  rasterImage(img, 0, 0, 1, 1)
  mtext(month.name[i], line = -2)
}
mtext('Seasonal variation of forest at NEON.D01.HARV.DP1.00033', font = 2, outer = TRUE)
```