---
title: "NEONphenology"
author: "K Duffy"
date: "10/16/2019"
output: html_document
---

```{r, silent=TRUE}
library(phenocamapi)
library(plotly)
library(phenocamr)
library(dplyr)
```

Let's start by pulling in a list of PhenoCam sites:



```{r}
phenos=get_phenos()
#and let's check the column names:
colnames(phenos)

```

Now let's filter for NEON sites:
```{r}
phenos=phenos%>%
  filter(group=='NEON AMERIFLUX')
head(phenos)
```


`

Example of data grab:

```{r}
phenocamr::download_phenocam(
  frequency = 3,
  veg_type = 'EN',
  roi_id = 1000,
  site = phenos$site[15],
  phenophase = TRUE,
  out_dir = "."
  )
#phenocamr::download_phenocam(
 # frequency = 3,
  #veg_type = 'GR',
  #roi_id = 1000,
  #site = phenos$site[15],
  #phenophase = TRUE,
  #out_dir = "."
  #)

```

```{r}
# load the time series data but replace the csv filename with whatever you downloaded
df <- read.table("NEON.D15.ONAQ.DP1.00033_SH_1000_3day.csv", header = TRUE, sep = ",")

# read in the transition date file
td <- read.table("NEON.D15.ONAQ.DP1.00033_SH_1000_3day_transition_dates.csv",
                 header = TRUE,
                 sep = ",")
```

```{r}
p = plot_ly() %>%
  add_trace(
  data = df,
  x = ~ as.Date(date),
  y = ~ smooth_gcc_90,
  name = 'Smoothed GCC',
  showlegend = TRUE,
  type = 'scatter',
  mode = 'line'
) %>% add_markers(
  data=df,
  x ~ as.Date(date),
  y = ~gcc_90,
  name = 'GCC',
  type = 'scatter',
  color ='#07A4B5',
  opacity=.5
)
p
```

###Threshold values

Let's subset the transition date (td) for each year when 25% of the greenness amplitude (of the 90^th) percentile is reached (threshold_25).

```{r}
# select the rising (spring dates) for 25% threshold of Gcc 90
spring <- td[td$direction == "rising" & td$gcc_value == "gcc_90",]

```

Now let's create a simple plot_ly line graph of the smooth Green Chromatic Coordinate (Gcc) and add points for transition dates:


```{r}
p = plot_ly() %>%
  add_trace(
  data = df,
  x = ~ as.Date(date),
  y = ~ smooth_gcc_90,
  name = 'PhenoCam GCC',
  showlegend = TRUE,
  type = 'scatter',
  mode = 'line'
) %>% add_markers(
  data= spring, 
  x = ~ as.Date(spring$transition_25, origin = "1970-01-01"),
  y = ~ spring$threshold_25,
  type = 'scatter',
  mode = 'marker',
  name = 'Spring Dates')
                
p
```

Now we can see the transition date for each year of interest and the annual patterns of greenness.

However, if you want more control over the parameters used during processing, you can run through the three default processing steps as implemented in download_phenocam() and set parameters manually.

Of particular interest is the option to specify your own threshold used in determining transition dates. 

What would be a reasonable threshold for peak greenness?  Or autumn onset?  Look at the ts dataset and phenocamr package and come up with a threshold.  Use the same code to plot it here:

```{r}
#print('code here')
#some hint code
#what does 'rising' versus 'falling' denote?
#what threshold should you choose?
#td <- phenophases("your_.csv",
#            internal = TRUE,
#            upper_thresh = 0.8)
fall <- td[td$direction == "falling" & td$gcc_value == "gcc_90",]

```



Let's load in a function to make plotting smoother.  I'm dropped it here in the markdown so that you can edit it and re-run it as you see fit:
```{r}
gcc_plot = function(gcc, spring, fall, plot_title){
  unix = "1970-01-01"

  p = plot_ly(
    data = gcc,
    x = ~ date,
    y = ~ gcc_90,
    showlegend = FALSE,
    type = 'scatter',
    mode = 'markers'
  ) %>%
    add_trace(
      y = ~ smooth_gcc_90,
      mode = "lines",
      line = list(width = 2, color = "rgb(120,120,120)"),
      name = "Gcc loess fit",
      showlegend = TRUE
    ) %>%
    # SOS spring
    # 10%
    add_trace(
      data = spring,
      x = ~ as.Date(transition_10),
      y = ~ threshold_10,
      mode = "markers",
      type = "scatter",
      marker = list(color = "#7FFF00", symbol = "circle"),
      name = "SOS (10%)",
      showlegend = TRUE
    ) %>%
    add_segments(x = ~ as.Date(transition_10_lower_ci),
                 xend = ~ as.Date(transition_10_upper_ci),
                 # y = ~ 0,
                 # yend = ~ 1,
                 y = ~ threshold_10,
                 yend = ~ threshold_10,
                 line = list(color = "#7FFF00"),
                 name = "SOS (10%) - CI"
    ) %>%
    # 25 %
    add_trace(
      x = ~ as.Date(transition_25),
      y = ~ threshold_25,
      mode = "markers",
      type = "scatter",
      marker = list(color = "#66CD00", symbol = "square"),
      showlegend = TRUE,
      name = "SOS (25%)"
    ) %>%
    add_segments(x = ~ as.Date(transition_25_lower_ci),
                 xend = ~ as.Date(transition_25_upper_ci),
                 y = ~ threshold_25,
                 yend = ~ threshold_25,
                 line = list(color = "#66CD00"),
                 name = "SOS (25%) - CI"
    ) %>%
    # 50 %
    add_trace(
      x = ~ as.Date(transition_50),
      y = ~ threshold_50,
      mode = "markers",
      type = "scatter",
      marker = list(color = "#458B00", symbol = "diamond"),
      showlegend = TRUE,
      name = "SOS (50%)"
    ) %>%
    add_segments(x = ~ as.Date(transition_50_lower_ci),
                 xend = ~ as.Date(transition_50_upper_ci),
                 y = ~ threshold_50,
                 yend = ~ threshold_50,
                 line = list(color = "#458B00"),
                 name = "SOS (50%) - CI"
    ) %>%
    
    # EOS fall
    # 50%
    add_trace(
      data = fall,
      x = ~ as.Date(transition_50),
      y = ~ threshold_50,
      mode = "markers",
      type = "scatter",
      marker = list(color = "#FFB90F", symbol = "diamond"),
      showlegend = TRUE,
      name = "EOS (50%)"
    ) %>%
    add_segments(x = ~ as.Date(transition_50_lower_ci),
                 xend = ~ as.Date(transition_50_upper_ci),
                 y = ~ threshold_50,
                 yend = ~ threshold_50,
                 line = list(color = "#FFB90F"),
                 name = "EOS (50%) - CI"
    ) %>%
    # 25 %
    add_trace(
      x = ~ as.Date(transition_25),
      y = ~ threshold_25,
      mode = "markers",
      type = "scatter",
      marker = list(color = "#CD950C", symbol = "square"),
      showlegend = TRUE,
      name = "EOS (25%)"
    ) %>%
    add_segments(x = ~ as.Date(transition_25_lower_ci),
                 xend = ~ as.Date(transition_25_upper_ci),
                 y = ~ threshold_25,
                 yend = ~ threshold_25,
                 line = list(color = "#CD950C"),
                 name = "EOS (25%) - CI"
    ) %>%
    # 10 %
    add_trace(
      x = ~ as.Date(transition_10),
      y = ~ threshold_10,
      mode = "markers",
      marker = list(color = "#8B6508", symbol = "circle"),
      showlegend = TRUE,
      name = "EOS (10%)"
    ) %>%
    add_segments(x = ~ as.Date(transition_10_lower_ci),
                 xend = ~ as.Date(transition_10_upper_ci),
                 y = ~ threshold_10,
                 yend = ~ threshold_10,
                 line = list(color = "#8B6508"),
                 name = "EOS (10%) - CI"
    )%>% 
    layout(title=plot_title)
  return (p)
}

```

```{r}

plot1 = gcc_plot(df, spring, fall)
plot1
```
Now I'll pull in the other two sites and plot up all 3 phenological signals:
```{r}

df <- read.table("NEON.D03.DSNY.DP1.00033_GR_1000_3day.csv", header = TRUE, sep = ",")

# read in the transition date file
td <- read.table("NEON.D03.DSNY.DP1.00033_GR_1000_3day_transition_dates.csv",
                 header = TRUE,
                 sep = ",")
spring <- td[td$direction == "rising" & td$gcc_value == "gcc_90",]
fall <- td[td$direction == "falling" & td$gcc_value == "gcc_90",]
plot2 = gcc_plot(df, spring, fall)
plot2
```
```{r}
df <- read.table("NEON.D16.ABBY.DP1.00033_EN_1000_3day.csv", header = TRUE, sep = ",")

# read in the transition date file
td <- read.table("NEON.D16.ABBY.DP1.00033_EN_1000_3day_transition_dates.csv",
                 header = TRUE,
                 sep = ",")
spring <- td[td$direction == "rising" & td$gcc_value == "gcc_90",]
fall <- td[td$direction == "falling" & td$gcc_value == "gcc_90",]
plot3 = gcc_plot(df, spring, fall)
plot3
```

Stack the plots:
```{r}
all_plot=subplot(nrows=3, plot1, plot2, plot3)
all_plot
```